Approximation as Differentiation notes

### 2025-02-24 notes/definitions.tex
Remove mention of zero objects for now.

\begin{proposition}
\item
\begin{itemize}
\item If $C$ has biproducts then it has products given by $(A \oplus B, p_A, p_B)$ and coproducts given by $(A
\oplus B, i_A, i_B)$.
\item If $C$ has products (or coproducts), then they are biproducts and thus $C$ is semi-additive.
\item If $C$ has a terminal (or initial) object then it is a zero object.
\end{itemize}
\end{proposition}

>>>>

If $C$ has biproducts then it has products given by $(A \oplus B, p_A, p_B)$ and coproducts given by $(A
\oplus B, i_A, i_B)$.

\begin{proposition}
\item
\begin{itemize}
\item If $C$ has products (or coproducts), then they are biproducts and thus $C$ is semi-additive.
\item If $C$ has a terminal (or initial) object then it is both initial and terminal.
\end{itemize}
\end{proposition}
